The LBRY Trending Algorithm

### 2021-11-17 tex/ms.tex
Equation
Some writing

\section{Introduction}
LBRY needs a trending algorithm to rank claims by `recent popularity',
preferably using on-chain information such as changes in support. An
intuitive idea is to have increases and decreases in overall support cause
a `spike' in the trending score, which then fades away over time
(assuming no further changes occur). This has formed the basis of all the
implementations that I have written.

@@

In 2021, Jack Robison rewrote a lot of the hub code to improve performance
and to ensure hub data integrity when a chain reorganisation occurs.

@@

\section{Nonlinearity --- the Spike Mass Function}\label{sec:spike_mass}

>>>>

\section{Introduction}
LBRY needs a trending algorithm to rank claims by `recent popularity',
preferably using on-chain information such as changes in support. An
intuitive idea is to have increases and decreases in overall support cause
a `spike' in the trending score, which then fades away over time
(assuming no further changes occur). This idea has formed the basis of all the
implementations that I have written.

@@

In 2021, Jack Robison rewrote a lot of the hub code to improve performance
and to ensure hub data integrity when a chain reorganisation occurs. The
backend now uses leveldb to store transaction and claim information, and
Elasticsearch to store claim information in a suitable form for clients to
query. Leveldb will be replaced with rocksdb soon.

@@

\section{Nonlinearity --- the Spike Mass Function}\label{sec:spike_mass}
As briefly discussed in the last section, a linear choice of spike mass
function might not be ideal. When we choose this function, we are making
a decision about how significant one amount of LBC at one time is, compared
to a different amount of LBC at a different time. For example, perhaps
1000 LBC right now should be considered as
significant as 10,000 LBC 12 hours ago.

Our final choice of spike mass function is complex. I will describe simpler
versions at first, which will help in motivating the final, complicated, choice.
\begin{align}
M(\ell_t, \ell_{t+1}) &=

\end{align}
